\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2023-07-31 manuscript/manuscript.tex
minor edits on new content and added blind option

\documentclass[12pt, letterpaper, titlepage]{article}

@@

\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}

\author{Anthony Zeimbekakis\\
%   \href{mailto:anthony.zeimbekakis@uconn.edu}
% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
  Elizabeth Schifano\\
  Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

\begin{document}
\maketitle

@@

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is widely employed to assess the
goodness-of-fit of a hypothezized continuous distribution to a sample.
Despite its popularity, the test is frequently in the literature and
practice. While originally intended for independent, continuous data with
precisely specified hypothesized distributions, it is erroneously applied to
scenarios with dependent, discrete, or rounded data, with hypothesized
distributions requiring estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when the 
hypothesized distribution has parameters that need to be estimated.
-conservative outcome when estimating such parameters. 
We demonstrate misuses of the one-sample KS test in
three scenarios through simulation studies:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
For each scenario, we provide remedies for practical applications using
appropriate bootstrap approaches.
The whole demonstration can be used as hands-on education materials on both
goodness-of-fit tests and bootstrap.

@@

@@

The contribution of this paper is a demonstration of misuses of the one-sample
KS test in three scenarios and their remedies in practice. Contrary to the
assumptions within the statistics community that anyone familiar with the
relevant literature would be ``misusing'' the KS test, there is still a
considerable journey ahead in educating students and practitioners from diverse
fields on the proper utilization of the KS test and similar tests. The scenarios
that we consider are where:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
In each scenario, the misuse is performed and the impacts are shown. Then, a
remedy is detailed and performed alongside the misuse to show its positive
effects. Specifically, unspecified parameters are handled by parametric
bootstrap; serial dependence is handled by introducing a working autoregressive
moving average (ARMA) model that preserves the serial dependence for a wide
range of dependence structures.
In order to set up the demonstrations, simulated data are used
throughout. The remedies are also performed on various families of
distributions. An R implementation of the proposed methods will be available
after the paper is published.

@@

The three kinds of misuses of the KS test for one-sample goodness-of-fit that we
demonstrated here are commonly seen in practice. With the aid of computing tools
such as R, they can be easily demonstrated in classroom teaching. Practitioners
need to be aware of the assumptions of the standard one-sample KS test that the
hypothesized distribution is completely specified and that the data are
independent. When these assumptions are not met, naive applications of the test
are no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and nonparametric bootstrap can restore
the size of the test. The nonparametric version has long been developed too but
is lesser known \citep{babu2004goodness}. In the case of serially dependent data,
our semiparametric bootstrap procedure with a working dependence structure
controlled by an automatically selected ARMA model restores the size of the test
for a wide range of dependence structures.
When both assumptions are violated, i.e., where the data has serial 
dependence and the parameters must be fitted, a combination of the two
individual remedies shows good results. The misuses of the KS tset are also seen
in practice with other goodness-of-fit tests based on the empirical distribution
function, such as the Anderson—Darling test or the Cramér—von Mise test, which
are known to be superior to KS in certain respects \citep{stephens2017tests}. We
expect that similar bootstrap remedies can be developed. Statisticians living in
an ivory tower tend to be doubt that anyone would be misusing the KS test as we
illustrated given that such situations are very well-known in the statistics
literature. It is our experience, however, that much effort is needed in
propagating many knowns in the statistics community to the real wild world
through innovative and impactful education. Such effort may be more valuable
than developing more advanced methods that no one would use in practice.

The semiparametric bootstrap procedure with a working ARMA dependence structure
is not a complete solution and has limitations. When the true serial dependence
can be well approximated by an ARMA model, the model selection process could be
avoided by using a computationally easier and theoretically more attractive
autoregressive sieve, i.e., autore-gressive models the order of which increases
simultaneously with the sample size at a suitably slower rate than the sample
size \citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
When the true serial dependence
structure cannot be well approximated by an ARMA model with normally distributed
error terms, the remedy may not restore the size of the test. The working
dependence structure is essentially the normal copula uniquely determined by the
ARMA model with normal errors. Some copulas are quite different from the normal
copula. For example, extreme value copulas have tail dependence, which is not
provided by normal copulas.
Using a normal copula to approximate an extreme value copula may not capture the
true serial dependence structure that is needed to restore the size of the
test. A block version of the nonparametric bootstrap \citep{babu2004goodness},
which avoids specification of a working dependence structure, would be more
desirable.

>>>>

\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper, titlepage]{article}

@@

% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{1}

%\title{On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit}
%
%\author{Anthony Zeimbekakis\\
%%   \href{mailto:anthony.zeimbekakis@uconn.edu}
%% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
  %Elizabeth D.  Schifano\\
  %Jun Yan\\[1ex]
  %Department of Statistics, University of Connecticut\\
%}
%\date{}

\begin{document}
%\maketitle

\if0\blind
{
  \title{\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample 
	Goodness-of-Fit}
  \author{Anthony Zeimbekakis, %\\
%   \href{mailto:anthony.zeimbekakis@uconn.edu}
% {\nolinkurl{anthony.zeimbekakis@uconn.edu}}\\
  Elizabeth D. Schifano, %\\
  Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample 
	Goodness-of-Fit}
\end{center}
  \bigskip
} \fi

@@

\begin{abstract}
The Kolmogorov--Smirnov (KS) test is widely employed to assess the
goodness-of-fit of a hypothezized continuous distribution to a sample.
Despite its popularity, the test is frequently misused in the literature and
practice. While originally intended for independent, continuous data with
precisely specified hypothesized distributions, it is erroneously applied to
scenarios with dependent, discrete, or rounded data, with hypothesized
distributions requiring estimated parameters. For example, it has been
``discovered'' multiple times that the test is too conservative when the 
hypothesized distribution has parameters that need to be estimated.
We demonstrate misuses of the one-sample KS test in
three scenarios through simulation studies:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
For each scenario, we provide remedies for practical applications using
appropriate bootstrap approaches.
The whole demonstration can be used as hands-on education materials on both
goodness-of-fit tests and bootstrap.

@@

%\doublespace

@@

The contribution of this paper is a demonstration of misuses of the one-sample
KS test in three scenarios and their remedies in practice. Contrary to the
assumptions within the statistics community that anyone familiar with the
relevant literature would not be ``misusing'' the KS test, there is still a
considerable journey ahead in educating students and practitioners from diverse
fields on the proper utilization of the KS test and similar tests. The scenarios
that we consider are where:
1) the hypothesized distribution has unspecified parameters;
2) the data are serially dependent; and
3) a combination of the first two scenarios.
In each scenario, the misuse is performed and the impacts are shown. Then, a
remedy is detailed and performed alongside the misuse to show its positive
effects. Specifically, unspecified parameters are handled by parametric
bootstrap; serial dependence is handled by introducing a working autoregressive
moving average (ARMA) model that preserves the serial dependence for a wide
range of dependence structures.
In order to set up the demonstrations, simulated data are used
throughout. The remedies are also performed on various families of
distributions. An R implementation of the proposed methods will be available
after the paper is published.

@@

The three kinds of misuses of the KS test for one-sample goodness-of-fit that we
demonstrated here are commonly seen in practice. With the aid of computing tools
such as R, they can be easily demonstrated in classroom teaching. Practitioners
need to be aware of the assumptions of the standard one-sample KS test that the
hypothesized distribution is completely specified and that the data are
independent. When these assumptions are not met, naive applications of the test
are no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and nonparametric bootstrap can restore
the size of the test. The nonparametric version has long been developed too but
is lesser known \citep{babu2004goodness}. In the case of serially dependent data,
our semiparametric bootstrap procedure with a working dependence structure
controlled by an automatically selected ARMA model restores the size of the test
for a wide range of dependence structures.
When both assumptions are violated, i.e., where the data has serial 
dependence and the parameters must be fitted, a combination of the two
individual remedies shows good results. The misuses of the KS tset are also seen
in practice with other goodness-of-fit tests based on the empirical distribution
function, such as the Anderson—Darling test or the Cramér—von Mise test, which
are known to be superior to KS in certain respects \citep{stephens2017tests}. We
expect that similar bootstrap remedies can be developed. Statisticians living in
an ivory tower tend to doubt that anyone would be misusing the KS test as we
illustrated given that such situations are very well-known in the statistics
literature. It is our experience, however, that much effort is needed in
propagating many knowns in the statistics community to the real wild world
through innovative and impactful education. Such effort may be more valuable
than developing more advanced methods that no one would use in practice.

The semiparametric bootstrap procedure with a working ARMA dependence structure
is not a complete solution and has limitations. When the true serial dependence
can be well approximated by an ARMA model, the model selection process could be
avoided by using a computationally easier and theoretically more attractive
autoregressive sieve, i.e., a sequence of autoregressive models the order of 
which increases
simultaneously with the sample size although at a suitably slower rate 
\citep[e.g.,][]{psaradakis2017distance, psaradakis2020normality}.
When the true serial dependence
structure cannot be well approximated by an ARMA model with normally distributed
error terms, the remedy may not restore the size of the test. The working
dependence structure is essentially the normal copula uniquely determined by the
ARMA model with normal errors. Some copulas are quite different from the normal
copula. For example, extreme value copulas have tail dependence, which is not
provided by normal copulas.
Using a normal copula to approximate an extreme value copula may not capture the
true serial dependence structure that is needed to restore the size of the
test. A block version of the nonparametric bootstrap \citep{babu2004goodness},
which avoids specification of a working dependence structure, would be more
desirable.
